|

### 2020-07-20 paper.Rmd
2D contours fixed.

@@

ggplot(proj_points, aes(x, y)) +
  geom_point(alpha=0.02) + 
  geom_density2d(bins = 7, contour_var = "count") +
  coord_fixed() +
  theme_bw() +
  facet_wrap(~p, labeller = labeller(name = lbl)) +
  guides(color = FALSE) +
  theme(axis.title.x=element_blank(), axis.title.y=element_blank())

>>>>

set.seed(2020)

@@

ggplot(proj_points, aes(x, y)) +
  geom_point(alpha=0.02) + 
  geom_density2d(bins = 7, contour_var = "ndensity") +
  coord_fixed() +
  theme_bw() +
  facet_wrap(~p, labeller = labeller(name = lbl)) +
  guides(color = FALSE) +
  theme(axis.title.x=element_blank(), axis.title.y=element_blank())
